Pillar 1 - Sequential Pattern Mining

### 2019-01-29 Pillar 1 - Sequential Pattern Mining.Rmd

```{r library, message = F}
library(tidyverse)

library(arulesSequences)
```

@@

## CSPADE Algorithm

@@

subsequences <- sequences %>%
  cspade(
    parameter = list(
      support = 0, # min support of a sequence
      maxsize = 1, # max number of items of an element of a sequence
      maxlen  = 2, # max number of element of a sequence
      mingap  = 1, # min time difference between consecutive element of a sequence
      maxgap  = 1e4, # max time difference between consecutive element of a sequence
      maxwin  = 1e4  # max time difference between any two elements of a sequence
      ),
    control = list(
      verbose = FALSE
      )
    )

>>>>

```{r library, message = F}
library(arulesSequences)

library(tidyverse)
```

@@

### CSPADE Algorithm

@@

subsequences <- sequences %>%
  cspade(
    parameter = list(
      support = 0.2, # min support of a sequence
      maxsize = 1, # max number of items of an element of a sequence
      maxlen  = 2, # max number of element of a sequence
      mingap  = 1, # min time difference between consecutive element of a sequence
      maxgap  = 1e4, # max time difference between consecutive element of a sequence
      maxwin  = 1e4  # max time difference between any two elements of a sequence
      ),
    control = list(
      verbose = FALSE
      )
    )
